EldersAIR: manuscript tables/figures

### 2022-08-05 health_analysis_itt.Rmd
new sensitivity analysis figure health itt paper

itt_health_results_confounders <- lmer(outcome ~ treatment + 
                                education + residents_smoke + home_sqm_2level +
                                burn_level + gender + chimney_clean + 
                                stove_grade + age + bmi + 
                                baseline_outcome + (1 | adult_id_char:home:cohort:area), 
                                data = bp_sys_data_2row)

@@

tidy_results_combined <- rbind(tidy_results_primary, tidy_results_confounders,
                               tidy_results_nohome, tidy_results_outliers)

@@

itt_plot_estimates <- tidy_results_combined %>%
  mutate(model = factor(model,
                        levels = c("Primary", "Confounders", "No Home Term",
                                   "Outliers Removed"))) %>% 
  ggplot(aes(group = term, shape = term)) +
    geom_point(aes(x=model, y=estimate), 
               position = position_dodge(width = 0.5), size = 4) +
    geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
                  position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
    geom_hline(yintercept = 0) +
    theme_bw() +  
    ggtitle(label = "Sys BP Model - ITT framework",
            subtitle = "ICC for subject = 0.58") +
    labs(y = "Estimate compared to Placebo") +
    labs(x = "", group = "", shape = "") +
    theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

itt_health_results_confounders <- lmer(outcome ~ treatment + 
                                education + residents_smoke + home_sqm_2level +
                                burn_level + gender + chimney_clean + stove_grade + 
                                age + bmi + 
                                baseline_outcome + (1 | adult_id_char:home:cohort:area), 
                                data = bp_dia_data_2row)

@@

tidy_results_combined <- rbind(tidy_results_primary, tidy_results_confounders,
                               tidy_results_nohome, tidy_results_outliers)

@@

@@

tidy_results_acceptable <- tidy(itt_health_results_acceptable, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment", "", term)) %>% 
  mutate(estimate = round((estimate), digits = 2),
         conf.low = round((conf.low), digits = 2),
         conf.high = round((conf.high), digits = 2)) %>% 
  dplyr::select(term, estimate, conf.low, conf.high, p.value) %>% 
  mutate(term = gsub("treatment", "", term),
         model = "Acceptable Sessions") %>% 
  dplyr::select(-p.value)
kable(tidy_results_acceptable)

@@

@@

@@

tidy_results_acceptable <- tidy(itt_health_results_acceptable, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment", "", term)) %>% 
  mutate(estimate = round((estimate), digits = 2),
         conf.low = round((conf.low), digits = 2),
         conf.high = round((conf.high), digits = 2)) %>% 
  dplyr::select(term, estimate, conf.low, conf.high, p.value) %>% 
  mutate(term = gsub("treatment", "", term),
         model = "Acceptable Sessions") %>% 
  dplyr::select(-p.value)
kable(tidy_results_acceptable)

@@

@@

@@

>>>>

itt_health_results_confounders <- lmer(outcome ~ treatment + 
                                education + residents_smoke + 
                                gender + stove_grade + 
                                age + bmi + 
                                baseline_outcome + (1 | adult_id_char:home:cohort:area), 
                                data = bp_sys_data_2row)

@@

tidy_results_combined_sbp <- rbind(tidy_results_primary, tidy_results_confounders,
                               tidy_results_nohome) %>% 
  mutate(outcome = "Systolic BP")

@@

itt_plot_estimates <- tidy_results_combined %>%
  mutate(model = factor(model,
                        levels = c("Primary", "Confounders", "No Home Term"))) %>% 
  ggplot(aes(group = term, shape = term)) +
    geom_point(aes(x=model, y=estimate), 
               position = position_dodge(width = 0.5), size = 4) +
    geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
                  position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
    geom_hline(yintercept = 0) +
    theme_bw() +  
    ggtitle(label = "Sys BP Model - ITT framework",
            subtitle = "ICC for subject = 0.58") +
    labs(y = "Estimate compared to Placebo") +
    labs(x = "", group = "", shape = "") +
    theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

itt_health_results_confounders <- lmer(outcome ~ treatment + 
                                education + residents_smoke + 
                                gender + stove_grade + 
                                age + bmi + 
                                baseline_outcome + (1 | adult_id_char:home:cohort:area), 
                                data = bp_dia_data_2row)

@@

tidy_results_combined_dbp <- rbind(tidy_results_primary, tidy_results_confounders,
                               tidy_results_nohome) %>% 
  mutate(outcome = "Diastolic BP")

@@

tidy_results_primary <- tidy(itt_health_results_primary, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment", "", term)) %>% 
  mutate(estimate = round((estimate), digits = 2),
         conf.low = round((conf.low), digits = 2),
         conf.high = round((conf.high), digits = 2)) %>% 
  dplyr::select(term, estimate, conf.low, conf.high, p.value) %>% 
  mutate(term = gsub("treatment", "", term),
         model = "All Sessions") %>% 
  dplyr::select(-p.value)
kable(tidy_results_primary)

@@

tidy_results_acceptable <- tidy(itt_health_results_acceptable, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment", "", term)) %>% 
  mutate(estimate = round((estimate), digits = 2),
         conf.low = round((conf.low), digits = 2),
         conf.high = round((conf.high), digits = 2)) %>% 
  dplyr::select(term, estimate, conf.low, conf.high, p.value) %>% 
  mutate(term = gsub("treatment", "", term),
         model = "Primary") %>% 
  dplyr::select(-p.value)
kable(tidy_results_acceptable)

itt_health_results_confounders <- lmer(outcome ~ treatment + 
                                education + residents_smoke + 
                                gender + stove_grade + 
                                age + bmi + 
                                baseline_outcome + (1 | adult_id_char:home:cohort:area), 
                                data = fvc_data_2row)

@@

tidy_results_combined_fvc <- rbind(tidy_results_primary, tidy_results_acceptable, 
                               tidy_results_confounders,
                               tidy_results_nohome) %>% 
  mutate(outcome = "FVC")

@@

tidy_results_acceptable <- tidy(itt_health_results_acceptable, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment", "", term)) %>% 
  mutate(estimate = round((estimate), digits = 2),
         conf.low = round((conf.low), digits = 2),
         conf.high = round((conf.high), digits = 2)) %>% 
  dplyr::select(term, estimate, conf.low, conf.high, p.value) %>% 
  mutate(term = gsub("treatment", "", term),
         model = "Primary") %>% 
  dplyr::select(-p.value)

@@

tidy_results_acceptable <- tidy(itt_health_results_acceptable, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment", "", term)) %>% 
  mutate(estimate = round((estimate), digits = 2),
         conf.low = round((conf.low), digits = 2),
         conf.high = round((conf.high), digits = 2)) %>% 
  dplyr::select(term, estimate, conf.low, conf.high, p.value) %>% 
  mutate(term = gsub("treatment", "", term),
         model = "Primary") %>% 
  dplyr::select(-p.value)
kable(tidy_results_acceptable)

itt_health_results_confounders <- lmer(outcome ~ treatment + 
                                education + residents_smoke + 
                                gender + stove_grade + 
                                age + bmi + 
                                baseline_outcome + (1 | adult_id_char:home:cohort:area), 
                                data = fev1_data_2row)

@@

tidy_results_combined_fev1 <- rbind(tidy_results_primary, tidy_results_acceptable, 
                               tidy_results_confounders,
                               tidy_results_nohome) %>% 
  mutate(outcome = "FEV1")

@@

tidy_results_combined_fev1_fvc_ratio <- rbind(tidy_results_primary, tidy_results_acceptable, 
                               tidy_results_confounders,
                               tidy_results_nohome) %>% 
  mutate(outcome = "FEV1/FVC Ratio")

@@

Manuscript figure
```{r}
tidy_results_combined <- rbind(tidy_results_combined_sbp, tidy_results_combined_dbp,
                               tidy_results_combined_fvc, tidy_results_combined_fev1,
                               tidy_results_combined_fev1_fvc_ratio)

itt_plot_estimates <- tidy_results_combined %>%
  mutate(model = factor(model,
                        levels = c("Primary", 
                                   "Confounders", "No Home Term",
                                   "All Sessions"))) %>% 
  mutate(outcome = factor(outcome,
                        levels = c("Systolic BP", "Diastolic BP",
                                   "FVC", "FEV1", "FEV1/FVC Ratio"),
                        labels = c("Systolic BP (mmHg)", "Diastolic BP (mmHg)",
                                   "FVC (mL)", "FEV1 (mL)", "FEV1/FVC Ratio"))) %>% 
  ggplot(aes(group = term, shape = term)) +
    geom_point(aes(x=model, y=estimate), 
               position = position_dodge(width = 0.5), size = 4) +
    geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
                  position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
    geom_hline(yintercept = 0) +
    theme_bw() +  
    labs(y = "Estimate compared to Placebo") +
    labs(x = "", group = "", shape = "") +
    theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          strip.text = element_text(size = 16, colour = "black"),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) +
    facet_wrap(~outcome, ncol = 1, scales = "free_y")
itt_plot_estimates

ggsave("elders_health_itt_plot.png", height = 9, width = 6)
```

### 2022-08-05 manuscript_tables_figures.Rmd
new sensitivity analysis figure health itt paper

>>>>

```{r}
obstruction_data <- elders_cleaned_dataset_by_visit %>% 
  arrange(home, adult_id_num, winter_id, sampling_visit) %>% 
  mutate(hypertension = if_else(bp_sys >= 140 | bp_dia >= 90, "Yes", "No"),
         obstruction = if_else(fev1_fvc_ratio < 0.7, "Yes", "No")) %>% 
  select(area, home, home_winter_id, winter_id, sampling_visit, adult_id_num,
         hypertension, obstruction, spiro_status, bp_sys, bp_dia) %>%
  filter(winter_id == 1) %>% 
  filter(spiro_status == "Acceptable") %>% 
  group_by(area, adult_id_num) %>% 
  mutate(obs_any = if_else(obstruction == "Yes" | lead(obstruction) == "Yes", "Yes", "No"),
         obs_any = if_else(is.na(obs_any), obstruction, obs_any)) %>% 
  ungroup() %>% 
  distinct(area, adult_id_num, .keep_all = TRUE)  
  count(obs_any)
obstruction_data

hypertension_data <- elders_cleaned_dataset_by_visit %>% 
  arrange(area, home, adult_id_num, winter_id, sampling_visit) %>% 
  filter(winter_id == 1) %>% 
  #filter(spiro_status == "Acceptable") %>% 
  group_by(area, adult_id_num) %>% 
  mutate(bp_sys = mean(bp_sys, na.rm = T),
         bp_dia = mean(bp_dia, na.rm = T),
         fev1_fvc_ratio = mean(fev1_fvc_ratio, na.rm = T)) %>% 
  mutate(hypertension_calc = if_else(bp_sys >= 140 | bp_dia >= 90, "Yes", "No"),
         obstruction = if_else(fev1_fvc_ratio < 0.7, "Yes", "No")) %>% 
  ungroup() %>% 
  select(area, home, home_winter_id, winter_id, sampling_visit, adult_id_num,
         hypertension, hypertension_calc, obstruction, spiro_status, bp_sys, bp_dia) %>%
  distinct(area, adult_id_num, .keep_all = T) %>% 
  #group_by(hypertension) %>% 
  count(hypertension_calc)
hypertension_data
```
